---
title: "individual_roost_use_figure_code"
author: "Caleb Ryan"
date: "23/02/2021"
output: html_document
---

This section of code should be run after individual_roost_use_aic 

This code uses data from both_use_reads.RDATA available in this repository. 
```{r}
load("/Users/caleb/OneDrive - University of Waterloo/Research/code/reader_merge_code/rdata/join.rdata")
```

Requires packages 'sjPlot' , 'dplyr' , 'tidyr' , 'ggplot2'

```{r}
library(sjPlot)
library(dplyr)
library(tidyr)
library(ggplot2)
library(glmmTMB)
library(ggpubr)
```


Code for creating sjPlots visualizing average individual variation from the mean
```{r}
pm_day = plot_model(day_roost_use_num_monthpit, type = "re", grid = FALSE , sort.est = "sort.all" , line.size = 0.5 , vline.color = "black",vline.size = 0.5, title = "", axis.title = "BLUP" , dot.size = 1.2)

pm_total = plot_model(roost_use_num_woage, type = "re", grid = FALSE , sort.est = "sort.all" , line.size = 0.5 , vline.color = "black",vline.size = 0.5, title = "", axis.title = "BLUP" , dot.size = 1.2)

# Start the graphics device
pdf(file = "ryan_2020_fig_1.pdf", useDingbats = FALSE)

# Plots
pm_day_plot = pm_day +  labs(title = "") + ylab("Deviation from the Mean") + xlab("Individual ID") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "grey"), axis.ticks.y=element_blank())

pm_total_plot = pm_total +  labs(title = "") + ylab("Deviation from the Mean") + xlab("Individual ID") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "grey"), axis.ticks.y=element_blank()) 

ggarrange(pm_day_plot + rremove("x.title"), pm_total_plot,  
          labels = c("A", "B"),
          ncol = 1, nrow = 2)
```


Code for creating linear regression comparing the individual random effect estimates for both roost metrics

```{r}
visited_modeldata = get_model_data(roost_use_num_woage, type = "re")

day_modeldata = get_model_data(day_roost_use_num_agepit , type = "re")

visited_modeldatasub = subset(visited_modeldata , select = c("estimate" , "term"))

day_modeldatasub = subset(day_modeldata , select = c("estimate" , "term"))

regress_data = left_join(day_modeldatasub , visited_modeldatasub , by = "term" )

summary(lm(regress_data$estimate.x ~ regress_data$estimate.y))
```

